### 2017-04-06 paper/evaluation.tex
removed some dummy data

\begin{center}
\fbox{
\begin{minipage}{8cm}
    \textit{Answering \numRQA{}:}~\emph{We conclude that
      time-consuming test suites are relatively frequent in
      open-source projects.  We found that \percentMedLongRunning{} of
      the \numSubjs{} projects we analyzed (\ie{}, over 1 in every 5
      projects) take at least 3 minutes to run and
      \percentLongRunning{} take at least 5 minutes to run.\Comment{
        (\ie, \numMedLong{} projects from \medg{} and \longg{}).}}
\end{minipage}
}
\end{center}

\vspace{1ex}
\begin{itemize}
    \item \numRQB. \textbf{\RQB}
\end{itemize}

@@

\begin{center}
\fbox{
\begin{minipage}{8cm}
    \textit{Answering \numRQB{}:}~\emph{Overall, results indicate that
    projects with a very small number of tests monopolizing end-to-end
    execution time were rare.}
\end{minipage}
}
\end{center}

@@

\begin{figure}[h!]
\centering
\resizebox{.48\textwidth}{!}{%
\begin{tabular}{llrrl}
\toprule
\emph{Group} & \emph{Subject} & \multicolumn{1}{c}{$T_s$} & \multicolumn{1}{c}{$T_p$} & $T_s/T_p$ \\%
\midrule%
Medium & BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.47m & 1.00x\\%
Medium & Apache \textbf{Flink} & 10.02m & 2.57m & 3.90x\\%
Long & Jenkins CI \textbf{Gerrit} Plugin & 76.32m & 40.31m &  1.89x\\%
Medium & Spotify \textbf{Helios} & 3.70m & 1.63m & 2.28x\\%  
Medium & \textbf{Javaslang} & 2.12m & 1.82m & 1.16x\\%
Medium & \textbf{Jcabi} GitHub & 2.75m & 0.30m & \cellcolor{lightgray}9.01x\\%
Medium & Hazelcast \textbf{Jet} & 8.26m & 3.67m & 2.25x\\%
Medium & Apache \textbf{Log4J2} & 4.73m & 8.21m & \cellcolor{lightgray}0.58x\\%
Medium & Jankotek \textbf{MapDB} & 10.51m & 8.58m & 1.23x\\%
\midrule
\textbf{total} &  &  &  & \avgSpeedup{}x\\
\bottomrule%
\end{tabular}}
\caption{Speedup (or slowdown) of parallel execution ($T_p$) over
  sequential execution ($T_s$).  Default parallel configuration of
  Maven is used.  Abbreviation of project names appear in bold face
  and highest slowdown/speedup appear in gray color.}
\label{tab:speedup}
\end{figure}

@@

Results indicate that, on average, parallel execution was
\avgSpeedup{} times faster compared to sequential execution.  We noted
two extreme cases: \CodeIn{Jcabi} and \CodeIn{Log4J2}.
The first when using the default parallel configuration, runs a
\textbf{C3} configuration with small test classes and big test
methods, allowing to run multiple methods and classes at once. The
high slowdown happens when big methods run sequentially.
The second when using the default parallel configuration, runs a
\textbf{FC0} configuration with small test classes and small test
methods, which is slowdown by the JVM creation overhead. This
configuration is useful to isolate each test method from each other.
\Luis{$\leftarrow$ rework this} \Fix{falar
  sobre o resultado geral dos speedups - elaborar menor e maior
  speedup... acho que so vale a pena discutir quando tiver conviccao
  dos 2 casos}

@@

To find dynamic evidence of parallelism, we ran the test suites from
our set of \numMedLong{} projects to output all key-value pairs of
Maven parameters.  To that end, we used the option~\CodeIn{-X} to
produce debug output and the option~\CodeIn{-DskipTests} to skip
execution of tests.  We observed that only bootstrapping the Maven
process suffices to discover which parallel configuration modes it
will use to run tests.  According to Maven's
documentation~\cite{maven-surefire-plugin}, a parallel configuration
depends either on (1) the parameter \CodeIn{parallel} to define the
parallelism mode within a JVM followed by the parameter
\CodeIn{threadCount} or (2) the parameter
\CodeIn{forkCount}\footnote{This parameter is named \CodeIn{forkMode}
  in old versions of Maven Surefire} to define the number of forked
JVMs.  As such, we captured, for each project, all related key-value
pairs of Maven parameters and mapped those pairs to one of the
possible parallelization modes.  For instance, if a given project
contains a module with the parameter
\CodeIn{<forkCount>1C</forkCount>}, the possible classifications are
\ForkSeq{} or \ForkParMeth{} depending on the presence and the value
of the parameter \CodeIn{parallel}.  If the parameter
\CodeIn{parallel} is set to \CodeIn{methods} the detected mode will be
\ForkParMeth{}.  Large projects may contain several test suites
distributed on different Maven modules potentially using different
configurations.  For those cases, we collected the Maven output from
each module discarding duplicates as to avoid inflating results. For
instance, if a project contains two modules using the same
configuration, we counted only one occurrence.

\Mar{---- estou aqui}

@@

%\begin{figure}[t!]
\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
    \footnotesize
    \centering
    \setlength{\tabcolsep}{2.5pt}
%    \resizebox{.48\textwidth}{!}{%
    \begin{tabular}{lrr}
        \toprule
        \emph{Subject} & \emph{\# of modules} & \emph{Mode}\\%
        \midrule%
        \Comment{BounceStorage }Chaos\Comment{ HTTP Proxy} & 1 &  \ParClassSeqMeth{}\\%
        \Comment{Apache }Flink & 74 & \ForkSeq{} \\%        
        \Comment{JenkinsCI }Gerrit\Comment{ Trigger Plugin} & 1 & \ForkSeq{}\\%
        \Comment{Spotify }Helios & 8 & \ForkSeq{}\\%
        Javaslang & 3 & \ParClassParMeth{}\\%
        Jcabi\Comment{ Github} & 1 & \ParClassParMeth{}\\%        
        \Comment{Hazelcast }Jet & 7 & \ForkSeq{}\\%
        \Comment{Apache Logging }Log4J2 & 25 & \ForkSeq{}\\%
        \Comment{Jankotek }MapDB & 1 & \ParClassParMeth{}\\%        
        \bottomrule%
    \end{tabular}
%    }
    \caption{Subjects with parallel test execution enabled by
    default.}
    \label{tab:freqmodes-dynamic}
    %\end{figure}
\end{wrapfigure}      
Figure~\ref{tab:freqmodes-dynamic} shows the projects we idendified
where parallelism is enabled by default.  Column ``\emph{Subject}''
indicates the name of the project, column ``\emph{\# of modules}''
indicates the number of detected modules containing tests, and column
``\emph{Mode}'' shows the parallel configuration mode used in those
modules (see Section~\ref{sec:modes}).  It came as a surprise the
observation that no project used distinct configurations in their
modules. Considering our set of \numMedLong{} projects, we found that
only \textbf{\numProjectsPar{}} of those projects had parallelism
enabled by default, with only configurations \ParClassSeqMeth{},
\ParClassParMeth{}, and \ForkSeq{} being used.  Configurations
\ParClassParMeth{} and \ForkSeq{} were the most popular among these
cases.  Note that these results under-approximate real usage of
parallelism as we used default parameters in our scripts to spawn the
Maven process.  That decision could prevent execution of particular
test modules.  
%\begin{figure}[h!]
%    \centering
%    \includegraphics[width=0.32\textwidth]{plots/barplot-modes-dynamic.pdf}
%    \caption{\label{fig:freqmodes-dynamic}\Fix{fix
%    caption}Distribution of parallel modes identified dynamically in a
%    subset of \numProjectsPar{} projects.  A project may have support
%    to more than one parallel mode. Also, a project may run only a
%    subset tests in parallel by default.}
%\end{figure}

\subsubsection{Presence of parallelism configurations in build files}
\label{sec:rqC-2}
Given the inherent limitation of dynamic monitoring to find evidence
of parallelism, we also looked for indication of parallelism in
\emph{pom.xml} files\Comment{ in the same sample set of \numMedLong{}
projects}. In principle, some projects can use parallel execution
although that is only activated when developers pass certain
parameters to the build process. For instance, it is possible to
create in Maven multiple configurations in the same build file and
select dynamically which one should be used.  We automatically parsed
\Fix{X} build files and we used the same approach to classify the
parsed configurations as in our previous analysis. Initially, we
noticed that our approach was unable to infer the parallel mode in
some projects because these projects do not declare a static value in
some parameters (\eg,
\CodeIn{<parallel>\$\{parallel.type\}</parellel>}). For these projects,
it is required to inform additional parameters to enable the parallel
mode in the command line (\eg, \CodeIn{mvn test
-Dparallel.type=classesAndMethods}). \Jbc{We wouldn't have FALSE
NEGATIVES if we considered this $\rightarrow$}To handle this case, we
considered all valid values for the parameter.

We found ten projects that use parallelism using this methodology.
Compared to the set of projects listed in Figure~\ref{tab:speedup}, we
found two new projects, namely: \CodeIn{Google Cloud\Comment{
    Platform} DataflowJavaSDK} (using configuration C3) and
\CodeIn{Mapstruct} (using configuration \ForkSeq{}).  Curiously, we
also found that project \CodeIn{Jcabi} was not detected using this
methodology.  That happened because \Mar{please, explain why}.
Considering the static and dynamic methods together, we found a total
of 11 distinct projects using parallelism, corresponding to the union
of the two subject sets.

\begin{center}
\fbox{
  \begin{minipage}{8cm}
      \textit{Answering \numRQC{}:}~\emph{Results indicate that test
        suite parallelization is underused.  Overall, only
        \percentParallel{} of costly projects (11 out of \numMedLong)
        use parallelism.}
  \end{minipage}
}
\end{center}

@@

To understand why developers prefer not use parallel test execution,
we considered \numNonParallel{} subjects that do not use parallel
configuration as default test execution from Section~\ref{sec:rqC-1} and elaborated a
quick survey to extent the comprehension about why developers do not
use parallel configuration. \Luis{describe how we created the survey}.
We first retrieve the last 20 commits from the project repository and
got the developers e-mails. In total, we sent an e-mail to
\emailsSent{} developers that recently contributed to the 
\numNonParallel{} projects, and we did not found any e-mail from
\Fix{??} projects using \CodeIn{git} tool.
\Luis{Here I want to say that I could not found any valid e-mail using
\textit{git log}}
There were \emailsAnswered{} replies from \emailsProjectsAnswered{}
projects, and \emailsFalseAnswers{} developers was not able to 
explain how the testing works or was not able to answer the survey.

The survey sent was composed by three open questions and one closed
question: (I) How long does it take for test to run in your
environment? Can you briefly define your setup? (II) Do you confirm
that your project does not run in parallel? (III) Select a reason for
not using parallelization: (a) I did not know it was possible; (b) I
was concerned with concurrency issues; (c) I use a continuous
integration server; (d) Some other reason. Please elaborate.

@@

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=.15\textwidth]{plots/survey.pdf}
    \caption{\Luis{todo}\label{fig:rq5-answers}}
\end{figure}

@@

\begin{figure}[h!]
\centering
\resizebox{.48\textwidth}{!}{%
\begin{tabular}{lrrrrrr}
\toprule
\emph{Subject} & \Seq{} & \SeqClassParMeth{} & \ParClassSeqMeth{} & \ParClassParMeth{} & \ForkSeq{} & \ForkParMeth{}\\%
\midrule%
BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
\bottomrule%
\end{tabular}}
\caption{\Fix{Tabela de eficiencia}}
\label{tab:rq6-efficiency}
\end{figure}

\begin{figure}[h!]
\centering
\resizebox{.48\textwidth}{!}{%
\begin{tabular}{lcrrrrr}
\toprule
\emph{Subject} & \emph{\# of tests} & \SeqClassParMeth{} & \ParClassSeqMeth{} & \ParClassParMeth{} & \ForkSeq{} & \ForkParMeth{}\\%
\midrule%
BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
\bottomrule%
\end{tabular}}
\caption{\Fix{Tabela de flakyness}}
\label{tab:rq6-efficiency}
\end{figure}

@@

%%  LocalWords:  RQ occurence parallelization Tradeoffs API readme th
%%  LocalWords:  mvn clearcut escapeinside xleftmargin untestable LTS
%%  LocalWords:  framexleftmargin CPUs Tahr sysstat gh Vagrantfile
%%  LocalWords:  javadoc isolcpus JUnit's JUnitCore Gligoric boxplots
%%  LocalWords:  outliers apache uber chaperone facebookarchive
%%  LocalWords:  linkbench

>>>>

\vspace{1ex}
\begin{center}
\fbox{
\begin{minipage}{8cm}
    \textit{Answering \numRQA{}:}~\emph{We conclude that
      time-consuming test suites are relatively frequent in
      open-source projects.  We found that \percentMedLongRunning{} of
      the \numSubjs{} projects we analyzed (\ie{}, over 1 in every 5
      projects) take at least 3 minutes to run and
      \percentLongRunning{} take at least 5 minutes to run.\Comment{
        (\ie, \numMedLong{} projects from \medg{} and \longg{}).}}
\end{minipage}
}
\end{center}
\vspace{1ex}

\begin{itemize}
    \item \numRQB. \textbf{\RQB}
\end{itemize}

@@

\vspace{1ex}
\begin{center}
\fbox{
\begin{minipage}{8cm}
    \textit{Answering \numRQB{}:}~\emph{Overall, results indicate that
    projects with a very small number of tests monopolizing end-to-end
    execution time were rare.}
\end{minipage}
}
\end{center}
\vspace{1ex}

@@

\begin{figure}[h!]
\centering
\resizebox{.48\textwidth}{!}{%
\begin{tabular}{llrrl}
\toprule
\emph{Group} & \emph{Subject} & \multicolumn{1}{c}{$T_s$} & \multicolumn{1}{c}{$T_p$} & $T_s/T_p$ \\%
\midrule%
Medium & BounceStorage \textbf{Chaos} HTTP Proxy  & 1.51m & 1.47m & 
    \cellcolor{lightgray}1.02x\\%
Medium & Apache \textbf{Flink} & 11.79m & 2.57m & 4.59x\\%
Long & Jenkins CI \textbf{Gerrit} Plugin & 51.19m & 40.31m &  1.26x\\%
Medium & Spotify \textbf{Helios} & 4.46m & 1.63m & 2.73x\\%  
Medium & \textbf{Javaslang} & 2.18m & 1.82m & 1.19x\\%
Medium & \textbf{Jcabi} GitHub & 2.76m & 0.30m &
    \cellcolor{lightgray}9.2x\\%
Medium & Hazelcast \textbf{Jet} & 8.26m & 3.67m & 2.25x\\%
Medium & Apache \textbf{Log4J2} & 8.24m & 8.21m & 
    \cellcolor{lightgray}1.00x\\%
Medium & Jankotek \textbf{MapDB} & 10.06m & 8.58m & 1.17x\\%
\midrule
\textbf{total} &  &  &  & \avgSpeedup{}x\\
\bottomrule%
\end{tabular}}
\caption{Speedup (or slowdown) of parallel execution ($T_p$) over
  sequential execution ($T_s$).  Default parallel configuration of
  Maven is used.  Abbreviation of project names appear in bold face
  and highest slowdown/speedup appear in gray color.}
\label{tab:speedup}
\end{figure}

@@

Results indicate that, on average, parallel execution was
\avgSpeedup{} times faster compared to sequential execution.  We noted
three extreme cases: \CodeIn{Chaos}, \CodeIn{Jcabi} and \CodeIn{Log4J2}.
The first, the default configuration is \textbf{C2}, however, the test is
composed of takes $>$99\% of the test time. In this case, when running
in sequential the execution time is almost the same as the parallel
execution.
The second when using the default parallel configuration, runs a
\textbf{C3} configuration with small test classes and big test
methods. In this case, a high slowdown is noticed when running those
big methods sequentially.
The third, runs parallel configuration in \Fix{80\%} of the project
modules, however, the test time is dominated by one of the
sequentially running modules.
\Luis{$\leftarrow$ rework this} \Fix{falar
  sobre o resultado geral dos speedups - elaborar menor e maior
  speedup... acho que so vale a pena discutir quando tiver conviccao
  dos 2 casos}

@@

To find dynamic evidence of parallelism, we ran the test suites from
our set of \numMedLong{} projects to output all key-value pairs of
Maven parameters.  To that end, we used the option~\CodeIn{-X} to
produce debug output and the option~\CodeIn{-DskipTests} to skip
execution of tests.  We skipped execution of tests as we observed from
sampling that only bootstrapping the Maven process suffices to infer
which parallel configuration modes it will use to actually run the
tests.  It is also important to point that we used the default
configurations specified in the project.  We inferred parallel
configurations by searching for certain configuration parameters in
log files. According to Maven's
documentation~\cite{maven-surefire-plugin}, a parallel configuration
depends either on (1) the parameter \CodeIn{parallel} to define the
parallelism mode within a JVM followed by the parameter
\CodeIn{threadCount} or (2) the parameter
\CodeIn{forkCount}\footnote{This parameter is named \CodeIn{forkMode}
  in old versions of Maven Surefire} to define the number of forked
JVMs.  As such, we captured, for each project, all related key-value
pairs of Maven parameters and mapped those pairs to one of the
possible parallelization modes.  For instance, if a given project
contains a module with the parameter
\CodeIn{<forkCount>1C</forkCount>}, the possible classifications are
\ForkSeq{} or \ForkParMeth{}, depending on the presence and the value
of the parameter \CodeIn{parallel}.  If the parameter
\CodeIn{parallel} is set to \CodeIn{methods} the detected mode will be
\ForkParMeth{}.  Large projects may contain several test suites
distributed on different Maven modules potentially using different
configurations.  For those cases, we collected the Maven output from
each module discarding duplicates as to avoid inflating counts for
configuration modes that appear in several modules of the same
project. For instance, if a project contains two modules using the
same configuration, we counted only one occurrence.

@@

%\begin{figure}[t!]
\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
    \footnotesize
    \centering
    \setlength{\tabcolsep}{2.5pt}
%    \resizebox{.48\textwidth}{!}{%
    \begin{tabular}{lrr}
        \toprule
        \emph{Subject} & \emph{\# of modules} & \emph{Mode}\\%
        \midrule%
        \Comment{BounceStorage }Chaos\Comment{ HTTP Proxy} & 1/1 &  \ParClassSeqMeth{}\\%
        \Comment{Apache }Flink & 74/74 & \ForkSeq{} \\%        
        \Comment{JenkinsCI }Gerrit\Comment{ Trigger Plugin} & 1/1 & \ForkSeq{}\\%
        \Comment{Spotify }Helios & 8/8 & \ForkSeq{}\\%
        Javaslang & 3/3 & \ParClassParMeth{}\\%
        Jcabi\Comment{ Github} & 1/1 & \ParClassParMeth{}\\%        
        \Comment{Hazelcast }Jet & 7/14 & \ForkSeq{}\\%
        \Comment{Apache Logging }Log4J2 & 25/31 & \ForkSeq{}\\%
        \Comment{Jankotek }MapDB & 1/2 & \ParClassParMeth{}\\%        
        \bottomrule%
    \end{tabular}
%    }
    \caption{Subjects with parallel test execution enabled by
    default.}
    \label{tab:freqmodes-dynamic}
    %\end{figure}
\end{wrapfigure}      
Figure~\ref{tab:freqmodes-dynamic} shows the projects we idendified
where parallelism is enabled by default in Maven.  Column
``\emph{Subject}'' indicates the name of the project, column
``\emph{\# of modules}'' indicates the fraction of modules containing
tests that use the configuration of parallelism mentioned in column
``\emph{Mode}''.  We note that, considering these projects, the
modules that do not use the configuration cited use the sequential
configuration \Seq{}.  For example, six modules (=31-25) from Log4J2
use sequential configuration.

It came as a surprise the observation that
no project used distinct configurations in their modules. Considering
our set of \numMedLong{} projects, we found that only
\textbf{\numProjectsPar{}} of those projects had parallelism enabled
by default, with only configurations \ParClassSeqMeth{},
\ParClassParMeth{}, and \ForkSeq{} being used.  Configurations
\ParClassParMeth{} and \ForkSeq{} were the most popular among these
cases.  Note that these results under-approximate real usage of
parallelism as we used default parameters in our scripts to spawn the
Maven process.  That decision could prevent execution of particular
test modules.
%\begin{figure}[h!]
%    \centering
%    \includegraphics[width=0.32\textwidth]{plots/barplot-modes-dynamic.pdf}
%    \caption{\label{fig:freqmodes-dynamic}\Fix{fix
%    caption}Distribution of parallel modes identified dynamically in a
%    subset of \numProjectsPar{} projects.  A project may have support
%    to more than one parallel mode. Also, a project may run only a
%    subset tests in parallel by default.}
%\end{figure}

%% Recall that some projects can use parallel execution that is only
%% activated when developers pass certain parameters to the build
%% process. For instance, it is possible to create in Maven multiple
%% configurations in the same build file and select dynamically which one
%% should be used.

\subsubsection{Static checking}
\label{sec:rqC-2}
Given the inherent limitation of dynamic monitoring to find evidence
of parallelism, we also looked for indication of parallelism in build
files\Comment{ in the same sample set of \numMedLong{} projects}.  We
parsed all \emph{pom.xml} files under the project's directory and used
the same approach as in our previous analysis to classify
configurations.  We noticed initially that our approach was unable to
infer the configuration mode for cases where the decision depends on
the input (\eg,
\CodeIn{<parallel>\$\{parallel.type\}</parallel>}). For these
projects, the tester needs to provide additional parameters in the
command line to enable parallelization (\eg, \CodeIn{mvn test
  -Dparallel.type=classesAndMethods}). To handle those case, we
considered all possible values for the parameter (in this case,
\CodeIn{\$\{parallel.type\}}).  It is also important to note that this
approach is not immune to false negatives, which can ocurr when
\emph{pom.xml} files are encapsulated in jar files or downloaded from
the network.  Consequently, this static checking is complementary to
the dynamic checking, previously presented.

Overall, we found, using this methodology, ten projects that use
parallelism.  Compared to the set of projects listed in
Figure~\ref{tab:speedup}, we found two new projects, namely:
\CodeIn{Google Cloud\Comment{ Platform} DataflowJavaSDK} (using
configuration C3) and \CodeIn{Mapstruct} (using configuration
\ForkSeq{}).  Curiously, we also found that project \CodeIn{Jcabi} was
not detected using this methodology.  That happened because this
project loads its \emph{pom.xml} file from a jar file that we did not
check.  Considering the static and dynamic methods together, we found
a total of 11 distinct projects using parallelism, corresponding to
the union of the two subject sets.

\vspace{1ex}
\begin{center}
\fbox{
  \begin{minipage}{8cm}
      \textit{Answering \numRQC{}:}~\emph{Results indicate that test
        suite parallelization is underused.  Overall, only
        \percentParallel{} of costly projects (11 out of \numMedLong)
        use parallelism.}
  \end{minipage}
}
\end{center}
\vspace{1ex}

@@

To answer this research question we surveyed developers involved in a
selection of projects from our benchmark with time-consuming test
suites.  The goal of the survey is to better comprehend developer's
attitude towards the use of parallelism as a mechanism to speedup
regression testing.  We surveyed developers from a total of
\Fix{x=83-11-y} projects.  From the initial list of \numMedLong{}
project, we discarded 11 projects that we knew a priori used
parallelization, and \Fix{y} projects that we could not find
developer's emails from commit logs.  From this list of projects, we
mined potential participants for our study.  More precisely, we
searched for developer's name and email from the last 20 commits to
the corresponding project repository.  Using this approach, we
identified a total of \emailsSent{} eligible participants.  Finally,
we sent plain-text e-mails to those developers with the survey.  In
total, \emailsAnswered{} developers replied but we discarded
\emailsFalseAnswers{} replies with subjective answers.  Considering
projects covered by the answers, a total of \emailsProjectsAnswered{}
projects (\percEmailsProjectsAnswered{} of the total) were represented
in those replies.  Note that multiple developers on each project
received emails.  We sent the following set of questions to
developers:

\begin{enumerate}
\item How long does it take for test to run in your environment? Can
  you briefly define your setup?
\item Do you confirm that your project does not run in parallel?
\item\label{questionThree} Select a reason for not using parallelization:
  \begin{enumerate}[label=\alph*)]
  \item I did not know it was possible
  \item I was concerned with concurrency issues
  \item I use a continuous integration server
  \item Some other reason. Please elaborate.
  \end{enumerate}
\end{enumerate}

@@

\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
    \centering
    \includegraphics[width=.15\textwidth]{plots/survey.pdf}
    \caption{\label{fig:rq5-answers}Summary of developer's answers to
      question~\ref{questionThree}.}
\end{wrapfigure}
The goal of the first two questions is to identify potential
discrepancies between the environment used to obtain our results and
environment of the developers.  Overall, we found that \Fix{...}

\Mar{... estou aqui ...}

@@

@@

\begin{figure}[h!]
\centering
\resizebox{.48\textwidth}{!}{%
\begin{tabular}{lrrrrrr}
\toprule
\emph{Subject} & \Seq{} & \SeqClassParMeth{} & \ParClassSeqMeth{} & \ParClassParMeth{} & \ForkSeq{} & \ForkParMeth{}\\%
\midrule%
BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
\bottomrule%
\end{tabular}}
\caption{\Fix{Tabela de eficiencia}}
\label{tab:rq6-efficiency}
\end{figure}

\begin{figure}[h!]
\centering
\resizebox{.48\textwidth}{!}{%
\begin{tabular}{lcrrrrr}
\toprule
\emph{Subject} & \emph{\# of tests} & \SeqClassParMeth{} & \ParClassSeqMeth{} & \ParClassParMeth{} & \ForkSeq{} & \ForkParMeth{}\\%
\midrule%
BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
\bottomrule%
\end{tabular}}
\caption{\Fix{Tabela de flakyness}}
\label{tab:rq6-efficiency}
\end{figure}

@@

%%  LocalWords:  RQ occurence parallelization Tradeoffs API readme th
%%  LocalWords:  mvn clearcut escapeinside xleftmargin untestable LTS
%%  LocalWords:  framexleftmargin CPUs Tahr sysstat gh Vagrantfile
%%  LocalWords:  javadoc isolcpus JUnit's JUnitCore Gligoric boxplots
%%  LocalWords:  outliers apache uber chaperone facebookarchive
%%  LocalWords:  linkbench priori
